---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Artist Menu Task

### Task Completition

```{r}
library(dplyr)
library(knitr)
library(lmerTest)
data <- read.csv("C:\\Users\\millerry\\Downloads\\ArtistMenuAnalysis.csv")
data2 <- filter(data, Experiment == 1)

library(lme4)
## Fit a mixed effects logistic regression model
## Outcome is whether subject failed to complete a task
fit <- glmer((valid == 0) ~ BAC + THC + factor(pageNum)  + (1 | ID), data = data2, family = "binomial")
kable(round(summary(fit)$coefficients, 4))

## Odds ratios and their 95% CIs
coefs <- summary(fit)$coefficients[,1]
ses <- summary(fit)$coefficients[,2]
kable(round(exp(data.frame(OR = coefs, LCL = coefs - 1.96*ses, UCL = coefs + 1.96*ses)), 4))
```

**Conclusions**:

- `PageNum` is extremely important, later pages = more likely not to complete the task
- `THC` is statistically significant, each 1% increase in blood THC leads to 6% increased odds of not completing a task (controlling for PageNum)

### Performance During Completed Tasks

```{r}
## Select control segments and valid experimental segments
data3 <- filter(data, (Experiment == 1 & valid == 1) | Experiment == 0)

table(data$valid, data$ID)

fit <- lmer(SD.Lane.Deviation ~ Experiment +  BAC + THC + Avg.Speed  +  (1| ID), data = data3)

#fit <- lmer(SD.Lane.Deviation ~ Experiment +  BAC + THC + Avg.Speed + THC:Experiment +  (1 | ID), data = data3)
#fit <- lmer(SD.Lane.Deviation ~ Experiment +  BAC + THC + Avg.Speed + BAC:Experiment +  (1 | ID), data = data3)
kable(round(summary(fit)$coefficients, 4))
```

**Conclusions**:

- Engagement in a Secondary Task significantly increases SD Lane Deviation
- Avg.Speed is another important predictor
- After adjusting for speed, neither THC or BAC modify the effect of Secondary Task Engagement on SD Lane Deviation


