---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(gridExtra)
library(lme4)
library(lmerTest)
library(dplyr)
library(tidyr)
library(knitr)
library(plotly)
```

```{r, echo = FALSE}
# Load data
# Artist Task ----
## Event time data
eventTimes <- read.csv("H:\\NIDA\\validArtistTimes.csv")
eventTimes$eventNum <- as.factor (eventTimes$eventNum)
eventTimes$pageNum <- as.factor (eventTimes$pageNum)
## Output variables for analysis
d3cp <- read.csv("H:\\NIDA\\validAnalysisArtist.csv")
d3n <- read.csv("H:\\NIDA\\AnalysisTasksNoEngage3.csv")

validd3cp <- filter (d3cp, valid == 1)
timeoutd3cp <- filter (d3cp, valid == 0)
```


# Artist Task Engagement Time 

Task time by pageNum:

```{r, echo = FALSE}
eventTimesByPage <- group_by(eventTimes, pageNum)
ggplot(eventTimes, aes(x = pageNum, y = total)) + geom_boxplot()
summarize(eventTimesByPage, 
          min = min(total, na.rm = TRUE), 
          Q1 = quantile(total, .25, na.rm = TRUE), 
          median = median(total, na.rm = TRUE), 
          Q3 = quantile(total, .75, na.rm = TRUE), 
          max = max(total, na.rm = TRUE))
```

Invalid vs Valid Artist Tasks:

```{r}
prop.table(table(eventTimes$DosingLevel, eventTimes$valid), 1)
```

# Artist Task output visuals

Standard deviation of lane deviation by dosage group and secondary task engagement (valid / invalid):

```{r, echo = FALSE}
p1 <- ggplot(data = validd3cp, aes(x = SD.Lane.Deviation, fill = factor(Experiment))) + geom_density(alpha = .5) + facet_wrap( ~ DosingLevel) + labs(fill = "Secondary Task", title = "Lane Deviation for valid artist task")
p2 <- ggplot(data = timeoutd3cp, aes(x = SD.Lane.Deviation, fill = factor(Experiment))) + geom_density(alpha = .5) + facet_wrap( ~ DosingLevel) + labs(fill = "Secondary Task", title = "Lane Deviation for invalid artist task")
grid.arrange(p1, p2, ncol = 2)
```

Boxplot version:

```{r, echo = FALSE}
# Sd Lane Deviation ----
ggplot(validd3cp, aes(x = DosingLevel, y = SD.Lane.Deviation, color = factor(Experiment))) + geom_boxplot() + labs(color = "Secondary Task", title = "Lane Deviation for valid artist task")
ggplot(timeoutd3cp, aes(x = DosingLevel, y = SD.Lane.Deviation, color = factor(Experiment))) + geom_boxplot() + labs(color = "Secondary Task", title = "Lane Deviation for invalid artist task")

# Avg Speed ----
ggplot(validd3cp, aes(x = DosingLevel, y = Avg.Speed, color = factor(Experiment))) + geom_boxplot() + labs(color = "Secondary Task", title = "Average Speed for valid artist task")
ggplot(timeoutd3cp, aes(x = DosingLevel, y = Avg.Speed, color = factor(Experiment))) + geom_boxplot() + labs(color = "Secondary Task", title = "Average Speed for invalid artist task")

# Sd Speed ----
ggplot(validd3cp, aes(x = DosingLevel, y = SD.Speed, color = factor(Experiment))) + geom_boxplot() + labs(color = "Secondary Task", title = "Standard Deviation ofSpeed for valid artist task")
ggplot(timeoutd3cp, aes(x = DosingLevel, y = SD.Speed, color = factor(Experiment))) + geom_boxplot() + labs(color = "Secondary Task", title = "Standard Deviation of Speed for invalid artist task")
```

**Conclusions**:

- Standard Deviation of Lane Deviation is much higher when engaged in secondary task (artist-menu search)
- This visual ignores pairing of segments/participants

### Paired (trt/control) version:

```{r, echo = FALSE}
diff <- validd3cp[validd3cp$Experiment == 1, ]$SD.Lane.Deviation - validd3cp[validd3cp$Experiment == 0, ]$SD.Lane.Deviation
diff_speed <- validd3cp[validd3cp$Experiment == 1, ]$Avg.Speed - validd3cp[validd3cp$Experiment == 0, ]$Avg.Speed
speed_ctrl <- validd3cp[validd3cp$Experiment == 0, ]$Avg.Speed
speed_trt <- validd3cp[validd3cp$Experiment == 1, ]$Avg.Speed 
df <- data.frame(diff_speed = diff_speed, diff_SD_lane_pos = diff, 
                 DosingLevel = validd3cp[validd3cp$Experiment == 1, ]$DosingLevel,
                 THC = validd3cp[validd3cp$Experiment == 1, ]$THC,
                 BAC = validd3cp[validd3cp$Experiment == 1, ]$BAC,
                 SubjectID = validd3cp[validd3cp$Experiment == 1, ]$ID,
                 pageNum = validd3cp[validd3cp$Experiment == 1, ]$pageNum)
ggplot(df, aes(x = DosingLevel, y = diff_SD_lane_pos)) + geom_boxplot(outlier.shape = NA) + geom_jitter(width = .15) + geom_abline(intercept = 0, slope = 0, lty = "dashed") + labs(y = "Paired within subject difference")
```

**Conclusions**:

- Within each experiment condition individual subject performance is worse when engaged in secondary task

### Within Subject Performance Differences by Condition

```{r, echo = FALSE}
df2 <- separate(df, col = DosingLevel, into = c("THC_Condition","ALC_Condition"), sep = -1)
p1 <- ggplot(df2, aes(x = factor(SubjectID), y = diff_SD_lane_pos, color = THC_Condition, pch = ALC_Condition, text = paste("CTRL speed:", round(speed_ctrl,2), "<br> TASK speed:", round(speed_trt,2), "<br> Speed change:", round(diff_speed,2)))) + 
  geom_point() + labs(x = "Subject ID", y = "Paired Difference in Std Lane Dev")
ggplotly(p1, tooltip = "text")
```

**Conclusions**:

- Some (but not all) of the instances where performance was better while engaged in the secondary task had slower speeds during the task
- Difficult to gauge condition effects from this plot

## Tables
Artist/Menu task segments available for analysis for each of the 19 subjects:

```{r, echo = FALSE}
tab1 <- table(df$SubjectID, df$DosingLevel)
rownames(tab1) <- paste("Subject ID",rownames(tab1))
tab1 <- addmargins(tab1)
kable(tab1)
```

### Marginal Statistics

Marginally, there is a statistically significant effect of secondary task engagement (for most Dose/Page Num) on standard deviation of lane deviation (p-values are from paired t-tests within subject/event):

```{r, echo = FALSE}
res <- df %>% group_by(DosingLevel, pageNum) %>% summarize(mean_SDL = mean(diff_SD_lane_pos),
                                                           sd_SDL = sd(diff_SD_lane_pos), n = n(),
                                           p_value = pmin(1,round(2*pnorm(-abs(mean(diff_SD_lane_pos))/
                                                                     (sd(diff_SD_lane_pos)/sqrt(n()))), 5)))
signif <- function(inp){
                if(inp >= .1) " "
                else if (inp < .1 & inp >= .05) "."
                else if (inp < .05 & inp >= .01) "*"
                else if (inp< .01 & inp >= .001) "**"
                else if (inp< .001) "***"
}
res$signif <- apply(matrix(res$p_value, ncol = 1), 1, signif)
kable(res)
```

## Models

### Model 1 - Base Model

$$y_{ij} = \beta_0 + \gamma_i + \beta_1 SecTask_{ij} + \beta_2 DoseXM_{ij} + \beta_3 DoseYM_{ij} + \ldots + \epsilon_{ij}$$

- $y_{ij}$ = Standard Deviation of lane deviation for subject $i$ at dosing level $j$
- $\gamma_i$ = subject specific random intercept
- $SecTask_{ij}$ = dummy variable indicating observation measures performance during secondary task (1 = sec task, 0 = control segment)
- $DoseAA_{ij}$ = dummy variable for dose = "AA" (1 = specified dose, 0 = reference group)
    - In our models we will re-define the reference group such that all dose effects are positive

```{r}
validd3cp$Dose_Grp <- relevel(validd3cp$DosingLevel, ref = "ZP")
fit <- lmer(data = validd3cp, SD.Lane.Deviation ~ Dose_Grp +  Experiment  + (1 | ID))
fit_sum <- summary(fit)
kable(round(fit_sum$coefficients, 4))
kable(round(anova(fit), 4))
```

```{r}
fit <- lmer(data = validd3cp, SD.Lane.Deviation ~ THC + BAC + Experiment  + (1 | ID))
fit_sum <- summary(fit)
kable(round(fit_sum$coefficients, 4))
kable(round(anova(fit), 4))
```

**Conclusions**:

- Significant effect of secondary task engagement on standard deviation of lane deviation
- No effect of experimental condition

- A few problems with this model:
    - Doesn't adjust for differences in speed
    - Skewed distribution of `SD.Lane.Deviation`
    - Treats all 3 secondary tasks as the same
    - It also isn't looking for effect modification by `Dose_Grp`

### Model 2 - Log-transformed outcome, control for pageNum and Avg.Speed

```{r}
fit <- lmer(data = validd3cp, log2(SD.Lane.Deviation) ~ relevel(DosingLevel, ref = "XM") + 
              factor(pageNum)  + Avg.Speed + Experiment + (1 | ID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit), 4))
```

```{r}
fit <- lmer(data = validd3cp, log2(SD.Lane.Deviation) ~ THC + BAC + 
              factor(pageNum)  + Avg.Speed + Experiment + (1 | ID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit), 4))
```

**Conclusions**:

- When we separate effect of THC and BAC, THC has P-value 0.0368
- Experiment and Avg.Speed has significant effect (P-value = 0.0000)

### Model 3 - Log-transformed outcome, control for pageNum and Avg.Speed, test for effect modification

- Does `Dose_Grp` modify the performance deteroration seen during secondary tasks?

```{r}
fit <- lmer(data = d3cp, log2(SD.Lane.Deviation) ~ relevel(DosingLevel, ref = "ZP") + 
              factor(pageNum)  + Avg.Speed + Experiment + 
              relevel(DosingLevel, ref = "ZP"):Experiment + (1 | ID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit),4))
```

```{r}
fit <- lmer(data = d3cp, log2(SD.Lane.Deviation) ~ THC + BAC + 
              factor(pageNum)  + Avg.Speed + Experiment +
              THC:Experiment + BAC:Experiment + (1 | ID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit),4))
```


### Model 4 - Paired Difference as Outcome

```{r}
fit <- lmer(data = df, diff_SD_lane_pos ~ relevel(DosingLevel, ref = "YM") + factor(pageNum) + diff_speed + (1 | SubjectID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit),4))
```

```{r}
fit <- lmer(data = df, diff_SD_lane_pos ~ THC + BAC + factor(pageNum) + diff_speed + (1 | SubjectID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit),4))
```
**Conclusions**:


### Model 5 - Avg Speed as Outcome

```{r}
fit <- lmer(data = validd3cp, Avg.Speed ~ relevel(DosingLevel, ref = "YP") + 
              factor(pageNum)  + Experiment   +  (1 | ID))
kable(round(summary(fit)$coefficients, 4))
kable(round(anova(fit),4))
```

**Conclusions**:

- Dosing condition has a highly significant impact on participant speed
- Secondary task engagement doesn't predict speed (p = 0.6104)
- No interaction between dosing and secondary task engagment (model testing this not shown, p > .9)

# Invalid vs Valid
