---
title: "NADS Presentation"
author: "Stella Lee, Ishaan Tibrewal"
date: "July 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(tidyverse)
library ("dplyr")
library(ggplot2)
```

# Cleaning Data

* filtering for disposition files --> artist/menu task
  * colored disposition files
* select necessary variables for analysis
```{r}

```

# Secondary Task Detection
* engagement point
  * used changepoint AMOC method (meanvar) with speed, lane deviation and minimum point
  * no invalid changepoint detection --> compare if engagement point was predicted after participant was incorrect

* exceptions:
  * two simulation with second instance not involved --> discard
```{r}

```
# Preminary Visualizations

## Question: We found that total time (from task available to complete) is longer as participant experience more task.
```{r}
eventTimes <- read.csv("H:\\NIDA\\eventTimesWith3.csv")
eventTimes$eventNum <- as.factor (eventTimes$eventNum)
eventTimesByInstance <- group_by(eventTimes, eventNum)
summarize(eventTimesByInstance, 
          min = min(total, na.rm = TRUE), 
          Q1 = quantile(total, .25, na.rm = TRUE), 
          median = median(total, na.rm = TRUE), 
          Q3 = quantile(total, .75, na.rm = TRUE), 
          max = max(total, na.rm = TRUE))

ggplot(eventTimes, aes(x = eventNum, y = total)) + geom_boxplot()
```

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
